Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-02-12 submission/conclusion.tex
last par, whitespace, misc stuff

\section{Conclusion}
\label{sxn:conc}

@@

\ncyan{
We conclude with a few thoughts on what a \emph{practical theory} of DNNs should look like.
\michael{MM TO DO.}
%
We distinguish between what we will call a
\emph{phenomenological theory}
(that describes empirical relationship of phenomena to each other, in a way which is consistent with fundamental theory, but is not directly derived from that theory)
and what can be called a 
\emph{first principles theory} 
(that is applicable to toy models, but that does not scale up to realistic systems if one includes realistic apsects of realistic systems).
%
For most complex highly-engineered systems (aside from complex AI/ML systems), one \emph{uses} phenomenological theory rather than first principles theory. 
(One does not try to solve the Schr\"odinger equation if one is interested in building a bridge or flying an airplane.)
%
Our results, which are based on our \emph{use} of sophisticated statistical mechanics theory to solve an important practical DNN problems, suggests that this approach should be of interest more generally for those interested in developing a practical DNN theory.
%\charles{it is the oppposite...ab initio theory scales quite well...it is the spherical cow models of physics and ML that do not scale. What we have is a semi-empirical theory.  We use real theory, but require empirical input, at least in the new stat mech work.  What we have introduced is a phenomenology, which to me is different from a semi-empirical or phenomenological theory  }
}

>>>>

\vspace{-1mm}
\section{Conclusion}
\label{sxn:conc}
%\vspace{-1mm}

@@

We conclude with a few comments on what a \emph{practical theory} of DNNs should look like.
To do so, we distinguish between two types of theories:
\emph{non-empirical or analogical theories}, in which one creates, often from general principles, a very simple toy model that can be analyzed rigorously, and one then argues that the model is relevant to the system of interest; and 
\emph{semi-empirical theories}, in which there exists a rigorous asymptotic theory, which comes with parameters, for the system of interest, and one then adjusts or fits those parameters to the finite non-asymptotic data.
A drawback of the former approach is that it typically makes very strong assumptions on the data, and the strength of those assumptions can limit the practical applicability of the theory.
Much of the work on the theory of DNNs focuses on the former type of theory.
Our approach focuses on the latter type of theory.
Our results, which are based on our \emph{use} of sophisticated statistical mechanics theory to solve important practical DNN problems, suggests that our approach should be of interest more generally for those interested in developing a practical DNN theory.
